Recruiting Chapter

### 2020-11-13 manuscript.Rmd
muddling through analyses...

library(kableExtra)
library(tidyverse)
```

@@

Figure \@ref(fig:two-mode-plot-privu) plots the two-mode network of visits by private colleges and universities to private high schools, with vertex color determined by community cluster.  The placement of college and high school vertices on an X-Y axis/coordinates is determined such that vertices with many direct and indirect ties are closer together. Although the process of placing vertices was separate from the process of determining community cluster, vertices within the same cluster tend to be closer to one another than those of different clusters. For example, the nonsectarian liberal arts colleges in Cluster 1 tend to be be close to one another and also relatively close to the highest concentration of private high schools in cluster 1, suggesting that these colleges visit substantially overlapping sets of private high schools. For Cluster 2, by contrast, Northwestern and Emory are relatively far from Tulane and Sewanee.

Addressing our two motivating research questions -- which schools receive visits from which colleges/universities and the extent to which visits are more likely to occur between organizations that share certain characteristics -- requires analyses that are more granular than Figure \@ref(fig:two-mode-plot-privu).

@@

```{r, ego-table-privu, echo = FALSE}
df <- readRDS('./assets/tables/table_ego_privu.RDS')
knitr::kable(
  df %>% select(-ID,-Characteristics), row.names = F, # select(-ID, -Characteristics)
  caption = 'ego table private colleges and universities') %>% landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

@@

```{r, ego-table-pubu, echo = FALSE}
df <- readRDS('./assets/tables/table_ego_pubu.RDS')
knitr::kable(
  df %>% select(-ID,-Characteristics), row.names = F, # select(-ID, -Characteristics)
  caption = 'ego table caption public universities') %>% landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

@@

```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
knitr::include_graphics('assets/figures/plot_2mode_privu.pdf')
```

@@

```{r rank-cluster1, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Academic rating of private high schools visited by selected colleges from cluster 1"}
knitr::include_graphics('assets/figures/rank_cluster1.pdf')
```

```{r race-cluster4, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Racial composition of visited private high schools, selected colleges"}
knitr::include_graphics('assets/figures/race_cluster4.pdf')
```

```{r two-mode-plot-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
knitr::include_graphics('assets/figures/plot_2mode_pubu.pdf')
```

```{r two-mode-plot-community, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
knitr::include_graphics('assets/figures/plot_2mode.pdf')
#https://stackoverflow.com/questions/15625990/how-to-set-size-for-local-image-using-knitr-for-markdown
```

>>>>

library(kableExtra)
library(tidyverse)
library(gridExtra)
```

@@

Figure \@ref(fig:plot-1mode-privu) plots the two-mode network of visits by private colleges and universities to private high schools, with vertex color determined by community cluster.  The placement of college and high school vertices on an X-Y axis/coordinates is determined such that vertices with many direct and indirect ties are closer together. Although the process of placing vertices was separate from the process of determining community cluster, vertices within the same cluster tend to be closer to one another than those of different clusters. For example, the nonsectarian liberal arts colleges in Cluster 1 tend to be be close to one another and also relatively close to the highest concentration of private high schools in cluster 1, suggesting that these colleges visit substantially overlapping sets of private high schools. For Cluster 2, by contrast, Northwestern and Emory are relatively far from Tulane and Sewanee.

Addressing our two motivating research questions -- which schools receive visits from which colleges/universities and the extent to which visits are more likely to occur between organizations that share certain characteristics -- requires analyses that are more granular than Figure \@ref(fig:plot-1mode-privu).

@@

```{r, ego-table-privu, echo = FALSE, include = FALSE, eval = FALSE}
df <- readRDS('./assets/tables/table_ego_privu.RDS')
knitr::kable(
  df %>% select(-ID,-Characteristics), row.names = F, # select(-ID, -Characteristics)
  caption = 'ego table private colleges and universities') %>% landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

@@

```{r, ego-table-pubu, echo = FALSE, include = FALSE, eval = FALSE}
df <- readRDS('./assets/tables/table_ego_pubu.RDS')
knitr::kable(
  df %>% select(-ID,-Characteristics), row.names = F, # select(-ID, -Characteristics)
  caption = 'ego table caption public universities') %>% landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

@@

```{r plot-1mode-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-privu"}
knitr::include_graphics('assets/figures/plot_1mode_privu.pdf')
```

```{r, fig.width=3.5, fig.height=3, echo = FALSE, message = FALSE}
plot_characteristic <- function(df, type, characteristics) {
  sub_df <- df %>% select(University, characteristics) %>%
    gather(key, value, characteristics) %>%
    mutate(value = parse_number(value))

  # colors <- sub_df$color[order(sub_df$University)]
  univ_order <- (df %>% arrange(Cluster, Type, as.numeric(Rank), University))$University  
  sub_df$University <- factor(sub_df$University, levels = rev(univ_order))

  ggplot(sub_df, aes(fill = key, y = value, x = University)) + 
    geom_bar(stat='identity', position = position_fill(reverse = TRUE)) +
    ggtitle('Title') +
    xlab('') + ylab('') +
    labs(fill = type) +
    scale_y_continuous(labels = scales::percent, expand = c(0, 0, 0.05, 0)) +
    theme(legend.position = 'top',
          legend.title = element_text(size = 6, face = 'bold'),
          legend.text = element_text(size = 6),
          legend.margin = margin(0, 0, 0, 0),
          legend.box.margin = margin(0, 0, -5, -30),
          legend.key.size = unit(0.3, 'cm'),
          panel.background = element_blank(),
          axis.ticks.y = element_blank(),
          # axis.text.y = element_text(color = rep(c('red', 'green', 'blue', 'yellow', 'black'), 5)),
          text = element_text(size = 8),
          plot.title = element_text(color = 'white')) +
    coord_flip()
}

type_vec <- c('privu', 'pubu')

for (i in 1:length(type_vec)) {
  ego_df <-readRDS(file.path('.', 'assets', 'tables', str_c('table_ego_', type_vec[i], '.RDS')))

  pdf(file.path('.', 'assets', 'figures', str_c('ego_network_figure_', type_vec[i], '.pdf')))
  par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
  par(mfrow=c(2, 2))

  a <- plot_characteristic(ego_df, 'Region', c('Northeast', 'Midwest', 'South', 'West'))
  b <- plot_characteristic(ego_df, 'Religion', c('Catholic', 'Conserv', 'Nonsect', 'Other'))
  c <- plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'))
  d <- plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'))

  grid.arrange(a, b, c, d, nrow=2, ncol=2)
  dev.off()

  # Need to use print() for ggplot inside loop in order for it to appear
  # https://stackoverflow.com/a/15678596/6373540
  #print(a)
  #print(b)
  #print(c)
  #print(d)
}
```

```{r ego-network-figure-privu, fig.align = 'center', echo = FALSE, fig.cap = "characteristics of private high schools visited by private colleges and universities"}
knitr::include_graphics('assets/figures/ego_network_figure_privu.pdf')
```

\newpage
```{r ego-network-figure-pubu, fig.align = 'center', echo = FALSE, fig.cap = "characteristics of private high schools visited by private colleges and universities"}
knitr::include_graphics('assets/figures/ego_network_figure_pubu.pdf')
```

@@

```{r plot-1mode-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-pubu"}
knitr::include_graphics('assets/figures/plot_1mode_pubu.pdf')
```

```{r plot-1mode-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-pubu out-of-state visits only"}
knitr::include_graphics('assets/figures/plot_1mode_pubu_outst.pdf')
```

```{r plot-1mode-all, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-all"}
knitr::include_graphics('assets/figures/plot_1mode_all.pdf')
```

```{r plot-1mode-all-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-all, out-of-state visits only for public universities"}
knitr::include_graphics('assets/figures/plot_1mode_all_pubu_outst.pdf')
```
